---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tabulate

<!-- badges: start -->
  [![R-CMD-check](https://github.com/dfalbel/tabulate/workflows/R-CMD-check/badge.svg)](https://github.com/dfalbel/tabulate/actions)
  <!-- badges: end -->

Tabulate is a thin wrapper around the [tabulate C++ library](https://github.com/p-ranav/tabulate).
It allows users to pretty print tables in the console, with support for different
font styles, colors, borders and etc. It also supports multi-bytes characters and
nesting tables.

## Installation

You can install the development version of tabulate from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("dfalbel/tabulate")
```

## Example

The following example shows basic functionality of tabulate. Like formatting and
coloring the output. Note that color and font styles are only suppported in platforms
that support ANSI strings. For a colored version of this table see this [link](file:///Users/dfalbel/Documents/tabulate/docs/articles/employees.html).

```{r}
library(tabulate)
department <- tabulate_table() %>% 
  table_add_row(c("Research", "Engineering"))

employees <- tabulate_table() %>% 
  table_add_row(
    c("Emp. ID", "First Name", "Last Name", "Department / Business Unit")) %>% 
  table_add_row(c("101", "Donald", "Patrick", "Finance")) %>% 
  table_add_row(
    c("102", "Rachel", "Williams", 
      "Marketing and Operational\nLogistics Planning")) %>% 
  table_add_row(c("103", "Ian", "Jacob", department))
  
employees[,1] %>% 
  format_font_style("bold") %>% 
  format_font_color("white") %>% 
  format_font_align("right")

employees[,4] %>% format_font_align("center")
```

```{r}
print(employees)
```

